# Material and Methods {-}
\chaptermark{Material and Methods}

```{r pckgs, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(kableExtra)
soilparam <- #load data
      read_delim("data/soil.csv",",",)

trt <- data.frame(
   Item = c("Amount,\nForm","Date\n(DAS)","Active\ningredient"),
   Herbicide = c("1 l/ha\nViper", "26","Diflufenican,\nFlorasulam,\nPenoxsulam"),
   Nitrogen = c("40,80\nkg/ha CAN","179,\n201", "Ammonium,\nNitrate,\nCalcium"),
   Magnesium = c("27 kg/ha\nMgO", "179", "Magnesium"),
   Sulfur = c("22 kg/h\nS", "179", "Sulfur"),
   Fungicides = c("1.5 l/ha\nChampion,\n1,0 l/ha\nSeguris", "210,\n232", "Epoxiconazol,\nBoscalid,\nIsopyrazam"),
   Regulators = c(" 0.3 l/ha\nCalma,\n0.5 l/ha\nCCC", "203", "Trinexapac\n-ethyl,\nChlormequat-\nchlorid")
)

# formatting 
   trt$Item <- linebreak(trt$Item, align ="l")
   trt$Herbicide <- linebreak(trt$Herbicide, align ="l")
   trt$Nitrogen <- linebreak(trt$Nitrogen, align ="l")
   trt$Magnesium <- linebreak(trt$Magnesium, align ="l")
   trt$Sulfur <-linebreak(trt$Sulfur, align ="l")
   trt$Fungicides <-linebreak(trt$Fungicides, align ="l")
   trt$Regulators <-linebreak(trt$Regulators, align ="l")
```


<!-- Required to number equations in HTML files -->
<script type="text/x-mathjax-config">
MathJax.Hub.Config({
  TeX: { equationNumbers: { autoNumber: "AMS" } }
});
</script>

This study determined how soil-living microorganisms are affected by inputs used in a conventional wheat cropping system. An agricultural field trial with wheat crops treated with conventionally used fertilizers, fungicides and growth regulators in Germany in 2019-2020 was performed. The treated crops were contrasted to control crops without the inputs. From the rhizosphere of the wheat crops samples were taken.   The genomic DNA in the samples was extracted and analyzed with quantitative polymerase chain reaction for their gene copy numbers of the targeted genes. Of interest were genes that produce enzymes for the nitrification of ammonia and 16S rRNA. Furthermore, this study employed generalized linear models using lme4 in R to estimate the effects of the fertilizers, fungicides and growth regulators on the gene copy numbers of the target genes. 

## Experimental design

### Field trial of winter-wheat in a randomized complete block design



An agricultural field in experimental station ZALF in Brandenburg, Germany (53°21'58.5"N 13°48'13.3"E) was used to study the effects of agriculture on soil microorganisms. The site has been used agriculturally for more than 30 years.  On the field, 3x7m plots were arranged in blocks. On 18.09.2019 winter wheat (*Triticum aestivum*, variety: RGT Reform) was sown in a density of 280 seeds/$\mathrm{m^2}$ on the assigned plots.  To avoid cross-over effects a buffer of rye (*Secale cereal*) was sown between blocks.
```{r soilParameters, echo=FALSE, message=FALSE}

kbl(soilparam, booktabs = T, caption = "Parameters and concentrations of chemical compounds in the experimental sites soil. Measured by a previous study using the same site.")%>% #print table 
  kable_styling(position = "center")#%>%
  #footnote(general= table_note, 
           #general_title = "Note.", footnote_as_chunk = T, threeparttable = T) #enforces linebreak for footnote
```
The chemical and physical quality of the fields soil was determined by a previous study (Table \@ref(tab:soilParameters)), which used the same field. Nitrogen and magnesium were measured by $\mathrm{CaCl_2}$ extraction. Phosphorus, potassium and sodium was measured by the double lactate method. Calcium was measured by the calcium-acetate-lactate method. pH was measured in a KCl suspension. Total carbon, nitrogen and sulfur were measured in an elemental analyzer.  The topsoil on the site is a loamy sand and ranges from Su3 to Sl3 across the blocks.






### Treatment of fertilizer, fungicides and growth regulators 
All plots were treated with an herbicide in form of *Viper™ Compact (Corteva Agriscience)* to suppress weeds at 26 days after sowing,. The herbicide was applied to lower nutritional and spatial struggle between the wheat crop and plants of no interest. 
Treatment was categorized into two factors. The components were nitrogen fertilizer, sulfur fertilizer, magnesium fertilizer, fungicides and growth regulators. The fertilizers were grouped into one treatment factor. Fungicide and growth regulators were grouped into a second treatment factor. Both factors were binary (Application [Yes] / No Application [No]) and crossed. Resulting in one treatment for each factor plus one crossed treatment and a control treatment. Fertilizer treatment was applied as calcium ammonium nitrate (CAN), magnesium oxide (MgO) and sulfur (S). All were added to the wheat plots 179 days after sowing. To secure the nitrogen supply in the fertilized plots, another dosage of CAN was added 201 days after sowing. Fungicides were applied to the wheat plots as *Champion ® (BASF)* at 210 and *Seguris \copyright (Syngenta)* at 232 days after sowing. Growth regulators were applied in form of *Calma (NuFarm)* and *CCC 720 (Bayer Agrar)* both at 203 days after sowing. A detailed list of the herbicide that was applied to all plots, fertilizers, fungicides and growth regulators and their active ingredients is listed in 

```{r Trt, echo=FALSE, message=FALSE}
library(kableExtra)
trt %>%
   kbl(booktabs = T,
       escape = F, 
       caption = "Listing of all treatment components used in the experiments. Days of application and their active ingredients included. Only herbicide applied to all plots. Fertilizers were grouped into one treatment factor. Fungicides and growth regulator into the other.")%>%
   add_header_above(c(" " = 2, "Fertilizers" = 3, " " = 2))%>%
   add_header_above(c(" " = 2, "Factor 1" = 3, "Factor 2" = 2))%>%
   footnote(general = "DAS = Days after sowing")#print table 
  #footnote(general= table_note, 
           #general_title = "Note.", footnote_as_chunk = T, threeparttable = T) #enforces linebreak for footnote
```
<!-- MATH and PHYSICS majors: Uncomment the following section -->
<!--
$$\sum_{j=1}^n (\delta\theta_j)^2 \leq {{\beta_i^2}\over{\delta_i^2 + \rho_i^2}}
\left[ 2\rho_i^2 + {\delta_i^2\beta_i^2\over{\delta_i^2 + \rho_i^2}} \right] \equiv \omega_i^2
$$

From Informational Dynamics, we have the following (Dave Braden):

After _n_ such encounters the posterior density for $\theta$ is

$$
\pi(\theta|X_1< y_1,\dots,X_n<y_n) \varpropto \pi(\theta) \prod_{i=1}^n\int_{-\infty}^{y_i}
   \exp\left(-{(x-\theta)^2\over{2\sigma^2}}\right)\ dx
$$

Another equation:

$$\det\left|\,\begin{matrix}%
c_0&c_1\hfill&c_2\hfill&\ldots&c_n\hfill\cr
c_1&c_2\hfill&c_3\hfill&\ldots&c_{n+1}\hfill\cr
c_2&c_3\hfill&c_4\hfill&\ldots&c_{n+2}\hfill\cr
\,\vdots\hfill&\,\vdots\hfill&
  \,\vdots\hfill&&\,\vdots\hfill\cr
c_n&c_{n+1}\hfill&c_{n+2}\hfill&\ldots&c_{2n}\hfill\cr
\end{matrix}\right|>0$$


Lapidus and Pindar, Numerical Solution of Partial Differential Equations in Science and
Engineering.  Page 54

$$
\int_t\left\{\sum_{j=1}^3 T_j \left({d\phi_j\over dt}+k\phi_j\right)-kT_e\right\}w_i(t)\ dt=0,
   \qquad\quad i=1,2,3.
$$

L\&P  Galerkin method weighting functions.  Page 55

$$
\sum_{j=1}^3 T_j\int_0^1\left\{{d\phi_j\over dt} + k\phi_j\right\} \phi_i\ dt
   = \int_{0}^1k\,T_e\phi_idt, \qquad i=1,2,3 $$

Another L\&P (p145)

$$
\int_{-1}^1\!\int_{-1}^1\!\int_{-1}^1 f\big(\xi,\eta,\zeta\big)
   = \sum_{k=1}^n\sum_{j=1}^n\sum_{i=1}^n w_i w_j w_k f\big( \xi,\eta,\zeta\big).
$$

Another L\&P (p126)

$$
\int_{A_e} (\,\cdot\,) dx dy = \int_{-1}^1\!\int_{-1}^1 (\,\cdot\,) \det[J] d\xi d\eta.
$$
-->

## Chemistry 101: Symbols

Chemical formulas will look best if they are not italicized. Get around math mode's automatic italicizing in LaTeX by using the argument `$\mathrm{formula here}$`, with your formula inside the curly brackets.  (Notice the use of the backticks here which enclose text that acts as code.)

So, $\mathrm{Fe_2^{2+}Cr_2O_4}$ is written `$\mathrm{Fe_2^{2+}Cr_2O_4}$`.

<!--
The \noindent command below does what you'd expect:  it forces the current line/paragraph to not indent. This was done here to match the format of the LaTeX thesis PDF.
-->

\noindent Exponent or Superscript: $\mathrm{O^-}$

\noindent Subscript: $\mathrm{CH_4}$

To stack numbers or letters as in $\mathrm{Fe_2^{2+}}$, the subscript is defined first, and then the superscript is defined.

\noindent Bullet: CuCl $\bullet$ $\mathrm{7H_{2}O}$


\noindent Delta: $\Delta$

\noindent Reaction Arrows: $\longrightarrow$ or  $\xrightarrow{solution}$

\noindent Resonance Arrows: $\leftrightarrow$

\noindent Reversible Reaction Arrows: $\rightleftharpoons$

### Typesetting reactions

You may wish to put your reaction in an equation environment, which means that LaTeX will place the reaction where it fits and will number the equations for you. 

\begin{equation}
  \mathrm{C_6H_{12}O_6  + 6O_2} \longrightarrow \mathrm{6CO_2 + 6H_2O}
  (\#eq:reaction)
\end{equation}

We can reference this combustion of glucose reaction via Equation \@ref(eq:reaction).

### Other examples of reactions

$\mathrm{NH_4Cl_{(s)}}$ $\rightleftharpoons$ $\mathrm{NH_{3(g)}+HCl_{(g)}}$

\noindent $\mathrm{MeCH_2Br + Mg}$ $\xrightarrow[below]{above}$ $\mathrm{MeCH_2\bullet Mg \bullet Br}$

## Physics

Many of the symbols you will need can be found on the math page <http://web.reed.edu/cis/help/latex/math.html> and the Comprehensive LaTeX Symbol Guide (<http://mirror.utexas.edu/ctan/info/symbols/comprehensive/symbols-letter.pdf>).

## Biology

You will probably find the resources at <http://www.lecb.ncifcrf.gov/~toms/latex.html> helpful, particularly the links to bsts for various journals. You may also be interested in TeXShade for nucleotide typesetting (<http://homepages.uni-tuebingen.de/beitz/txe.html>).  Be sure to read the proceeding chapter on graphics and tables.

