```{r include_packages_2, include = FALSE}
# This chunk ensures that the huskydown package is
# installed and loaded. This huskydown package includes
# the template files for the thesis and also two functions
# used for labeling and referencing
if(!require(devtools))
  install.packages("devtools", repos = "http://cran.rstudio.com")
if(!require(dplyr))
    install.packages("dplyr", repos = "http://cran.rstudio.com")
if(!require(ggplot2))
    install.packages("ggplot2", repos = "http://cran.rstudio.com")
if(!require(ggplot2))
    install.packages("bookdown", repos = "http://cran.rstudio.com")
if(!require(gauchodown)){
  library(devtools)
  devtools::install_github("benmarwick/gauchodown")
  }
library(gauchodown)
flights <- read.csv("data/flights.csv")
```


# Results {#ref-labels}

```{r chemly, echo=FALSE, error=FALSE,message=FALSE,results='asis'}
cat(knitr::knit_child("/sub/chemly.Rmd", quiet=TRUE))
#knits the calculations for chemical analysis
```

## Chemical analysis of soil and roots 


Nitrogen in the form of Nitrate (\ch{NO3-})

\clearpage

<!-- clearpage ends the page, and also dumps out all floats.
  Floats are things like tables and figures. -->


## Figures

Test

<!--
One thing that may be annoying is the way _R Markdown_ handles "floats" like tables and figures (it's really \LaTeX's fault). \LaTeX\ will try to find the best place to put your object based on the text around it and until you're really, truly done writing you should just leave it where it lies. There are some optional arguments specified in the options parameter of the `label` function.  If you need to shift your figure around, it might be good to look here on tweaking the options argument:  <https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions>

If you need a graphic or tabular material to be part of the text, you can just put it inline. If you need it to appear in the list of figures or tables, it should be placed in a code chunk.
-->


In the **R** chunk below, we will load in a picture stored as `uw.png` in our main directory.  We then give it the caption of "UW logo", the label of "uwlogo", and specify that this is a figure.  Make note of the different **R** chunk options that are given in the R Markdown file (not shown in the knitted document).

```{r uwlogo, fig.cap="UW logo"}

```

Here is a reference to the UW logo: Figure \@ref(fig:uwlogo).  Note the use of the `fig:` code here.  By naming the **R** chunk that contains the figure, we can then reference that figure later as done in the first sentence here.  We can also specify the caption for the figure via the R chunk option `fig.cap`.

\clearpage 

<!-- starts a new page and stops trying to place floats such as tables and figures -->

Below we will investigate how to save the output of an **R** plot and label it in a way similar to that done above.  Recall the `flights` dataset from Chapter \@ref(rmd-basics).  (Note that we've shown a different way to reference a section or chapter here.)  We will next explore a bar graph with the mean flight departure delays by airline from Portland for 2014.  Note also the use of the `scale` parameter which is discussed on the next page.

```{r delaysboxplot, warnings=FALSE, messages=FALSE, fig.cap="Mean Delays by Airline", fig.width=6}
flights %>% group_by(carrier) %>%
  summarize(mean_dep_delay = mean(dep_delay)) %>%
  ggplot(aes(x = carrier, y = mean_dep_delay)) +
  geom_bar(position = "identity", stat = "identity", fill = "red")
```

Here is a reference to this image: Figure \@ref(fig:delaysboxplot).

A table linking these carrier codes to airline names is available at <https://github.com/ismayc/pnwflights14/blob/master/data/airlines.csv>.

\clearpage

Next, we will explore the use of the `out.extra` chunk option, which can be used to shrink or expand an image loaded from a file by specifying `"scale= "`. Here we use the mathematical graph stored in the "subdivision.pdf" file.


Here is a reference to this image: Figure \@ref(fig:subd).  Note that `echo=FALSE` is specified so that the **R** code is hidden in the document.



## Footnotes and Endnotes

You might want to footnote something. ^[footnote text] The footnote will be in a smaller font and placed appropriately. Endnotes work in much the same way. 

## Bibliographies

Of course you will need to cite things, and you will probably accumulate an armful of sources. There are a variety of tools available for creating a bibliography database (stored with the .bib extension).  In addition to BibTeX suggested below, you may want to consider using the free and easy-to-use tool called Zotero. Some Zotero documentation is at <http://libguides.reed.edu/citation/zotero>.  In addition, a tutorial is available from Middlebury College at <http://sites.middlebury.edu/zoteromiddlebury/>.

_R Markdown_ uses _pandoc_ (<http://pandoc.org/>) to build its bibliographies.  One nice caveat of this is that you won't have to do a second compile to load in references as standard LaTeX requires. To cite references in your thesis (after creating your bibliography database), place the reference name inside square brackets and precede it by the "at" symbol.  For example, here's a reference to a book about worrying:  [@Molina1994].  This `Molina1994` entry appears in a file called `thesis.bib` in the `bib` folder.  This bibliography database file was created by a program called BibTeX.  You can call this file something else if you like (look at the YAML header in the main .Rmd file) and, by default, is to placed in the `bib` folder.  

For more information about BibTeX and bibliographies, see (<http://web.reed.edu/cis/help/latex/index.html>)^[@reedweb2007]. There are three pages on this topic:  _bibtex_ (which talks about using BibTeX, at <http://web.reed.edu/cis/help/latex/bibtex.html>), _bibtexstyles_ (about how to find and use the bibliography style that best suits your needs, at <http://web.reed.edu/cis/help/latex/bibtexstyles.html>) and _bibman_ (which covers how to make and maintain a bibliography by hand, without BibTeX, at <http://web.reed.edu/cis/help/latex/bibman.html>). The last page will not be useful unless you have only a few sources.

If you look at the YAML header at the top of the main .Rmd file you can see that we can specify the style of the bibliography by referencing the appropriate csl file.  You can download a variety of different style files at <https://www.zotero.org/styles>.  Make sure to download the file into the csl folder.

**Tips for Bibliographies**

- Like with thesis formatting, the sooner you start compiling your bibliography for something as large as thesis, the better. 
- The cite key (a citation's label) needs to be unique from the other entries.
- When you have more than one author or editor, you need to separate each author's name by the word "and" e.g. `Author = {Noble, Sam and Youngberg, Jessica},`.
- Bibliographies made using BibTeX (whether manually or using a manager) accept LaTeX markup, so you can italicize and add symbols as necessary.
- To force capitalization in an article title or where all lowercase is generally used, bracket the capital letter in curly braces.

## Anything else?

If you'd like to see examples of other things in this template, please [contact us](https://github.com/benmarwick/huskydown/issues/new) (email <bmarwick@uw.edu>) with your suggestions. We love to see people using _R Markdown_ for their theses, and are happy to help.

